Statistical Stopping Criteria for Active Learning in Systematic Review Screening

### 2019-10-17 manuscript/main.tex
jointplots

\usepackage{todonotes}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{url}
%\def\includegraphic{}
%\def\includegraphics{}

@@

	\begin{figure}
		\includegraphics[width=\linewidth]{../images/additional_burden}
		\caption{Additional burden for 20 random samples where the 95\% threshold has been reached, and the remaining documents are 1\%, 2\% or 5\% relevant, for different total numbers of documents.}
		\label{additional-burden}
	\end{figure}

@@

	\begin{figure}
		\includegraphics[width=\linewidth]{../images/burden_vs_misrecall}
		\caption{Additional burden ($y > 0$) and missed recall ($ y < 0 $) for the range of stopping criteria tested.}
		\label{additional-burden-missed-recall}
	\end{figure}

	\begin{figure}
		\includegraphics[width=\linewidth]{../images/wss_recall_burden_boxplot}
		\caption{Work saved, recall and additional burden across a variety of stopping criteria}
		\label{additional-burden-missed-recall-boxplots}
	\end{figure}

	\begin{figure}
	\includegraphics[width=\linewidth]{../images/results_hex}
	\caption{Work saved, recall across a variety of stopping criteria}
	\label{results-hex}
\end{figure}

	\begin{figure}
	\includegraphics[width=\linewidth]{../images/ab_recall_studies}
	\caption{Work saved, recall across a variety of stopping criteria}
	\label{ab_recall_studies}
\end{figure}

>>>>

\usepackage{todonotes}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{url}
\usepackage{subcaption}
%\def\includegraphic{}
%\def\includegraphics{}

@@

@@

    \begin{figure*}
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../images/jointplot_bir}
		\caption[Network2]%Example-Image
		{{\small Baseline Sampling}}    
		\label{fig:mean and std of net14}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{../images/jointplot_ih_50}
		\caption[]%
		{{\small 50 consecutive irrelevant results}}    
		\label{fig:mean and std of net24}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{../images/jointplot_hyper}
		\caption[]%
		{{\small Hypergeometric sampling \\}}    
		\label{fig:mean and std of net34}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{../images/jointplot_nrs}
		\caption[]%
		{{\footnotesize Pseudorandom hypergeometric sampling}}    
		\label{fig:mean and std of net44}
	\end{subfigure}
	\caption[ The average and standard deviation of critical parameters ]
	{\small The average and standard deviation of critical parameters: Region R4} 
	\label{fig:mean and std of nets}
\end{figure*}
